---
title: "Satellite imagery to flooding data"
author: "Dana Lanceman"
date: "2023-07-21"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Import and load packages}
#install.packages("raster")
#install.packages("stringr")
#install.packages("sf")

library("raster")
library("stringr")
library("sf")
```

# 1. Input data
We need to input the appropriate satellite data for each year (2010-2022) and location (Cumbung and Booligal).
We need green, red, NIR, SWIR 1 and SWIR 2 bands.
- for Landsat 4/5 and 7 data, these are band 2 (green), 3 (red), 4 (NIR), 5 (SWIR 1) and 7 (SWIR 2)
- for Landsat 8/9 data, these are band 3 (green), 4 (red), 5 (NIR), 6 (SWIR 1) and 7 (SWIR 2)

Naming format for data:
- Example name: LT05_L2SP_094084_20111104_20200820_02_T1_ST_QA
  - This is equivalent to SatelliteType_L2SP_Location_Date_SecondDate_02_T1_DataType***

Naming conventions for the satellite data:
- SatelliteType:
  - LT05 = Landsat 4/5
  - LE07 = Landsat 7
  - LC08 = Landsat 8/9
- Location
  - 094084 = Cumbung
  - 093083 and 093084
- Date 
  -YearMonthDay - date data was collected
- SecondDate
  - Not sure what this is, maybe when the data were processed?? But I don't think we need it.
- DataType***
  - This part is of various lengths (but will always start at the same position in the string as the previous sections are all standard lengths) and identifies which band or other data type the data is
  - SR_B1 = band 1, SR_B2 = band 2, etc.

```{r Input data - rasters}
# Set your working directory to the folder containing the TIFF files
setwd("C:/Users/z5204897/OneDrive - UNSW/Desktop/RA/Projects/2023_Lachlan_waterbird_and_flood_datasets_compilation/Raw Landsat data")

# List all the TIFF files in the folder
all_files <- list.files() # list all files, including those we don't care about
print(all_files) # check how file names are being read - looks like the extension TIF is capitalised, which we need to code for.

# Now list just the file names we're interested in - bands 2 to 7
# //d+ refers to a string of one or more digits (0-9)
file_list <- list.files(pattern = paste("^(LT05|LE07|LC08)_L2SP_\\d+_\\d+_\\d+_(02_)?T[1-2]_(SR|ST)_B[2-7]\\.TIF", sep = ""))
print(file_list)

# Function to extract relevant information from the filename - satellite, location, date, band
extract_info <- function(filename) {
  parts <- strsplit(filename, "_")[[1]] # the [[1]] extracts the character vector of the components of the file name, rather than creating a list that you have to access the character vector from within
  satellite <- paste0(substr(parts[1], 1, 1), substr(parts[1], nchar(parts[1]), nchar(parts[1])))  # Extract the first and fourth characters as satellite name (L5, L7, or L8)
  location <- parts[3]
  date <- parts[4]
  band <- gsub("(SR|ST)_", "", parts[length(parts)]) #gsub means substitute one thing for another
  band <- gsub("\\.TIF", "", band)
  return(list(satellite = satellite, location = location, date = date, band = band))
}

# Create empty lists to store the raster objects
cumbung_list <- list()
booligal_list <- list()

# Loop through the files and import the rasters, while naming them - Cumbung
for (filename in file_list) {
  info <- extract_info(filename)
  
  # Check if the band is in the desired list
  if (info$band %in% c("B2", "B3", "B4", "B5", "B6", "B7")) { 
    if(info$location %in% c("094084")) {
    raster_data <- raster(filename)
    
    # Name the raster object based on the extracted information
    raster_name <- paste(info$satellite, info$location, info$date, info$band, sep = "_")
    
    # Assign the raster object to the list with the specified name
    cumbung_list[[raster_name]] <- raster_data
    
    # Print a message to indicate successful import and naming
    cat("Imported and named", filename, "as", raster_name, "\n")
  } }
}

# Loop through the files and import the rasters, while naming them - Booligal
for (filename in file_list) {
  info <- extract_info(filename)
  
  # Check if the band is in the desired list
  if (info$band %in% c("B2", "B3", "B4", "B5", "B6", "B7")) { 
    if(info$location %in% c("093084", "093083")) {
    raster_data <- raster(filename)
    
    # Name the raster object based on the extracted information
    raster_name <- paste(info$satellite, info$location, info$date, info$band, sep = "_")
    
    # Assign the raster object to the list with the specified name
    booligal_list[[raster_name]] <- raster_data
    
    # Print a message to indicate successful import and naming
    cat("Imported and named", filename, "as", raster_name, "\n") #"\n" indicates new line, printing each on a new line
  } }
}


# now all of the rasters have been imported and stored in "cumbung_list" and "booligal_list"
```

```{r Input data - shapefiles}
cumbung <- st_read("C:/Users/z5204897/OneDrive - UNSW/Desktop/RA/Projects/2023_Lachlan_waterbird_and_flood_datasets_compilation/Boundaries/Cumbung_ecological.shp")
booligal <- st_read("C:/Users/z5204897/OneDrive - UNSW/Desktop/RA/Projects/2023_Lachlan_waterbird_and_flood_datasets_compilation/Boundaries/Booligal_ecological.shp")
```

# 2. Manipulate data

```{r Crop rasters to boundaries}
clipped_cumbung_list <- list()
for (raster_name in names(cumbung_list)) {
  raster_data <- cumbung_list[[raster_name]]
  clipped_raster <- mask(raster_data, cumbung)
  clipped_cumbung_list[[raster_name]] <- clipped_raster
  # Print a message to indicate successful clipping
  cat("Clipped", raster_name, "\n")
}

clipped_booligal_list <- list()
for (raster_name in names(booligal_list)) {
  raster_data <- booligal_list[[raster_name]]
  clipped_raster <- mask(raster_data, booligal)
  clipped_booligal_list[[raster_name]] <- clipped_raster
    # Print a message to indicate successful clipping
  cat("Clipped", raster_name, "\n")
}
```

Need to group rasters by date so multiple bands from the same date are associated with one another.

```{r Group rasters by date}
# need a new version of the extract info function that recognises the new file name format (we renamed the rasters)
# the name name format is: satellite_location_date_band

extract_info_2 <- function(filename) {
  parts <- strsplit(filename, "_")[[1]] # the [[1]] extracts the character vector of the components of the file name, rather than creating a list that you have to access the character vector from within
  satellite <- parts[1]
  location <- parts[2]
  date <- parts[3]
  band <- parts[4]
  return(list(satellite = satellite, location = location, date = date, band = band))
}

# Cumbung
grouped_rasters_cumbung <- list()
for (raster_name in names(clipped_cumbung_list)) {
  raster_data <- clipped_cumbung_list[[raster_name]]
  date <- extract_info_2(raster_name)$date
  band <- extract_info_2(raster_name)$band
  # Check if a list with the date already exists in grouped_rasters
  # And name items in the list according to their band 
  if (band %in% names(grouped_rasters_cumbung[[date]])) {
    # If it exists, add the raster_data to the existing list
    grouped_rasters_cumbung[[date]][[band]] <- c(grouped_rasters_cumbung[[date]][[band]], raster_data)
  } else {
    # If it doesn't exist, create a new list with the raster_data
    grouped_rasters_cumbung[[date]][[band]] <- list(raster_data)
  }
}

```

Bands of interest to calculate water index
- for Landsat 4/5 and 7 data, these are band 2 (green), 3 (red), 4 (NIR), 5 (SWIR 1) and 7 (SWIR 2)
- for Landsat 8/9 data, these are band 3 (green), 4 (red), 5 (NIR), 6 (SWIR 1) and 7 (SWIR 2)

# Up to here - errors below as you can't input a list into the calc function...

```{r troubleshooting}

grouped_rasters_cumbung[["20111104"]][["B3"]]
plot(grouped_rasters_cumbung[["20111104"]][["B3"]][[1]]) # plotting an empty raster

# try plotting a raster directly from the raw data
testRaster <- raster("C:/Users/z5204897/OneDrive - UNSW/Desktop/RA/Projects/2023_Lachlan_waterbird_and_flood_datasets_compilation/Raw Landsat data/LT05_L2SP_094084_20111104_20200820_02_T1_SR_B2.tif")
plot(testRaster) # plots correctly, so the program is not reading the rasters in the list correctly

# try plotting a raster from the original imported list
plot(cumbung_list[["L5_094084_20111104_B6"]]) # plots correctly, issue is not from this stage.

# try plotting the clip layer
plot(cumbung) # this plots with five plots according to attribute, not sure if that's normal
cumbung # getting info about this shapefile, it looks like its geometry is in latitude rather than a projected coordinate system, which may have stuffed things up when cropping?

# try plotting a clipped raster
plot(clipped_cumbung_list[["L5_094084_20111104_B6"]]) # empty.. I think it was the clipping that stuffed things around due to different coordinate systems

# try water index from below using rasters from the original images, rather than the clipped images

water_index <- overlay(cumbung_list[["L5_094084_20111104_B2"]], cumbung_list[["L5_094084_20111104_B3"]], cumbung_list[["L5_094084_20111104_B4"]], cumbung_list[["L5_094084_20111104_B5"]], cumbung_list[["L5_094084_20111104_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(water_index) # success!! woohoo
```


```{r Calculate water index - Landsat 4/5 and 7 data}

# list all the possible dates
cumbung_dates <- names(grouped_rasters_cumbung)
cumbung_dates

# new list for results 
water_index_results <- list()


# use the overlay function to do calculations using multiple rasters
water_index <- overlay(grouped_rasters_cumbung[["20111104"]][["B2"]][[1]], grouped_rasters_cumbung[["20111104"]][["B3"]][[1]], grouped_rasters_cumbung[["20111104"]][["B4"]][[1]], grouped_rasters_cumbung[["20111104"]][["B5"]][[1]], grouped_rasters_cumbung[["20111104"]][["B7"]][[1]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(water_index)

setwd("C:/Users/z5204897/OneDrive - UNSW/Desktop/RA/Projects/2023_Lachlan_waterbird_and_flood_datasets_compilation/R/waterbird_lachlan")
#writeRaster(water_index,filename = "Export/water_index_20111104_cumbung.tif", format="GTiff", overwrite = TRUE)

```


```{r}
# Function - Landsat 8/9
Water_index_L89 <- function(b2, b3, b4, b5, b7) {
  water_index <- 1.7204+171*b3+3*b4-70*b5-45*b6-71*b7
  return(water_index)
}


    # Print a message to indicate successful calculation
  cat("Calculated water index for", raster_name, "\n")  
```

