---
title: "Satellite imagery to flooding data"
author: "Dana Lanceman"
date: "2023-07-21"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Import and load packages}
#install.packages("raster")
#install.packages("stringr")
#install.packages("sf")

library("raster")
library("stringr")
library("sf")
```

# 1. Input data
We need to input the appropriate satellite data for each year (2010-2023) and location (Cumbung and Booligal).
We need green, red, NIR, SWIR 1 and SWIR 2 bands.
- for Landsat 4/5 and 7 data, these are band 2 (green), 3 (red), 4 (NIR), 5 (SWIR 1) and 7 (SWIR 2)
- for Landsat 8/9 data, these are band 3 (green), 4 (red), 5 (NIR), 6 (SWIR 1) and 7 (SWIR 2)

Naming format for data:
- Example name: LT05_L2SP_094084_20111104_20200820_02_T1_ST_QA
  - This is equivalent to SatelliteType_L2SP_Location_Date_SecondDate_02_T1_DataType***

Naming conventions for the satellite data:
- SatelliteType:
  - LT05 = Landsat 4/5
  - LE07 = Landsat 7
  - LC08 = Landsat 8/9
- Location
  - 094084 = Cumbung
  - 093083 and 093084
- Date 
  -YearMonthDay - date data was collected
- SecondDate
  - Not sure what this is, maybe when the data were processed?? But I don't think we need it.
- DataType***
  - This part is of various lengths (but will always start at the same position in the string as the previous sections are all standard lengths) and identifies which band or other data type the data is
  - SR_B1 = band 1, SR_B2 = band 2, etc.

```{r Input data - rasters}
# Set your working directory to the folder containing the TIFF files
setwd("C:/Users/z5204897/OneDrive - UNSW/Desktop/RA/Projects/2023_Lachlan_waterbird_and_flood_datasets_compilation/Raw Landsat data")

# List all the TIFF files in the folder
all_files <- list.files() # list all files, including those we don't care about
print(all_files) # check how file names are being read - looks like the extension TIF is capitalised, which we need to code for.

# Now list just the file names we're interested in - bands 2 to 7
# //d+ refers to a string of one or more digits (0-9)
file_list <- list.files(pattern = paste("^(LT05|LE07|LC08|LC09)_L2SP_\\d+_\\d+_\\d+_(02_)?T[1-2]_(SR|ST)_B[2-7]\\.TIF", sep = ""))
print(file_list)

# Function to extract relevant information from the filename - satellite, location, date, band
extract_info <- function(filename) {
  parts <- strsplit(filename, "_")[[1]] # the [[1]] extracts the character vector of the components of the file name, rather than creating a list that you have to access the character vector from within
  satellite <- paste0(substr(parts[1], 1, 1), substr(parts[1], nchar(parts[1]), nchar(parts[1])))  # Extract the first and fourth characters as satellite name (L5, L7, or L8)
  location <- parts[3]
  date <- parts[4]
  band <- gsub("(SR|ST)_", "", parts[length(parts)]) #gsub means substitute one thing for another
  band <- gsub("\\.TIF", "", band)
  return(list(satellite = satellite, location = location, date = date, band = band))
}

# Create empty lists to store the raster objects
cumbung_list <- list()
booligal_list <- list()

# Loop through the files and import the rasters, while naming them - Cumbung
for (filename in file_list) {
  info <- extract_info(filename)
  
  # Check if the band is in the desired list
  if (info$band %in% c("B2", "B3", "B4", "B5", "B6", "B7")) { 
    if(info$location %in% c("094084")) {
    raster_data <- raster(filename)
    
    # Name the raster object based on the extracted information
    raster_name <- paste(info$satellite, info$location, info$date, info$band, sep = "_")
    
    # Assign the raster object to the list with the specified name
    cumbung_list[[raster_name]] <- raster_data
    
    # Print a message to indicate successful import and naming
    cat("Imported and named", filename, "as", raster_name, "\n")
  } }
}

# Loop through the files and import the rasters, while naming them - Booligal
for (filename in file_list) {
  info <- extract_info(filename)
  
  # Check if the band is in the desired list
  if (info$band %in% c("B2", "B3", "B4", "B5", "B6", "B7")) { 
    if(info$location %in% c("093084", "093083")) {
    raster_data <- raster(filename)
    
    # Name the raster object based on the extracted information
    raster_name <- paste(info$satellite, info$location, info$date, info$band, sep = "_")
    
    # Assign the raster object to the list with the specified name
    booligal_list[[raster_name]] <- raster_data
    
    # Print a message to indicate successful import and naming
    cat("Imported and named", filename, "as", raster_name, "\n") #"\n" indicates new line, printing each on a new line
  } }
}


# now all of the rasters have been imported and stored in "cumbung_list" and "booligal_list"
```

```{r Input data - shapefiles}
cumbung <- st_read("C:/Users/z5204897/OneDrive - UNSW/Desktop/RA/Projects/2023_Lachlan_waterbird_and_flood_datasets_compilation/Boundaries/Cumbung_ecological.shp")
booligal <- st_read("C:/Users/z5204897/OneDrive - UNSW/Desktop/RA/Projects/2023_Lachlan_waterbird_and_flood_datasets_compilation/Boundaries/Booligal_ecological.shp")
```


# 2. Calculate water index - Landsat 4/5/7

Bands of interest to calculate water index
- for Landsat 4/5 and 7 data, these are band 2 (green), 3 (red), 4 (NIR), 5 (SWIR 1) and 7 (SWIR 2)

Landsat 4/5/7 data:
- Cumbung - 2010, 2011, 2012, 2020
- Booligal 093083 - 2010, 2011, 2012
- Booligal 093084 - 2010, 2011, 2012

```{r Calculate water index - Landsat 4/5/7 - Cumbung}

# 2010
# use Dec 3 as it has less cloud cover
wi_cumbung_2010 <- overlay(cumbung_list[["L5_094084_20101203_B2"]], cumbung_list[["L5_094084_20101203_B3"]], cumbung_list[["L5_094084_20101203_B4"]], cumbung_list[["L5_094084_20101203_B5"]], cumbung_list[["L5_094084_20101203_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(wi_cumbung_2010)


# 2011
wi_cumbung_2011 <- overlay(cumbung_list[["L5_094084_20111104_B2"]], cumbung_list[["L5_094084_20111104_B3"]], cumbung_list[["L5_094084_20111104_B4"]], cumbung_list[["L5_094084_20111104_B5"]], cumbung_list[["L5_094084_20111104_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(wi_cumbung_2011)


# 2012
wi_cumbung_2012 <- overlay(cumbung_list[["L7_094084_20121114_B2"]], cumbung_list[["L7_094084_20121114_B3"]], cumbung_list[["L7_094084_20121114_B4"]], cumbung_list[["L7_094084_20121114_B5"]], cumbung_list[["L7_094084_20121114_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(wi_cumbung_2012)
# looks dodgy, probably because it's L7 - might need to try a different image


# 2020
wi_cumbung_2020 <- overlay(cumbung_list[["L7_094084_20201018_B2"]], cumbung_list[["L7_094084_20201018_B3"]], cumbung_list[["L7_094084_20201018_B4"]], cumbung_list[["L7_094084_20201018_B5"]], cumbung_list[["L7_094084_20201018_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(wi_cumbung_2020)
# looks very dodgy, probably because it's L7...

```

```{r Calculate water index - Landsat 4/5/7 - Booligal 093083}
# 2010
wi_bool_2010_1 <- overlay(booligal_list[["L5_093083_20101008_B2"]], booligal_list[["L5_093083_20101008_B3"]], booligal_list[["L5_093083_20101008_B4"]], booligal_list[["L5_093083_20101008_B5"]], booligal_list[["L5_093083_20101008_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(wi_bool_2010_1)
# there's cloud cover but I think it's north of the wetland

# 2011
# redownloading these data
wi_bool_2011_1 <- overlay(booligal_list[["L5_093083_20111011_B2"]], booligal_list[["L5_093083_20111011_B3"]], booligal_list[["L5_093083_20111011_B4"]], booligal_list[["L5_093083_20111011_B5"]], booligal_list[["L5_093083_20111011_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(wi_bool_2011_1)

# 2012
wi_bool_2012_1 <- overlay(booligal_list[["L7_093083_20121022_B2"]], booligal_list[["L7_093083_20121022_B3"]], booligal_list[["L7_093083_20121022_B4"]], booligal_list[["L7_093083_20121022_B5"]], booligal_list[["L7_093083_20121022_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(wi_bool_2012_1)
# looks weird because of Landsat 7
```

```{r Calculate water index - Landsat 4/5/7 - Booligal 093084}
# 2010
wi_bool_2010_2 <- overlay(booligal_list[["L5_093084_20101008_B2"]], booligal_list[["L5_093084_20101008_B3"]], booligal_list[["L5_093084_20101008_B4"]], booligal_list[["L5_093084_20101008_B5"]], booligal_list[["L5_093084_20101008_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(wi_bool_2010_2)

# 2011
wi_bool_2011_2 <- overlay(booligal_list[["L5_093084_20111011_B2"]], booligal_list[["L5_093084_20111011_B3"]], booligal_list[["L5_093084_20111011_B4"]], booligal_list[["L5_093084_20111011_B5"]], booligal_list[["L5_093084_20111011_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(wi_bool_2011_2)


# 2012
wi_bool_2012_2 <- overlay(booligal_list[["L7_093084_20121022_B2"]], booligal_list[["L7_093084_20121022_B3"]], booligal_list[["L7_093084_20121022_B4"]], booligal_list[["L7_093084_20121022_B5"]], booligal_list[["L7_093084_20121022_B7"]], fun = function(B2, B3, B4, B5, B7) {
  return(1.7204+171*B2+3*B3-70*B4-45*B5-71*B7)
})
plot(wi_bool_2012_2)
# looks weird because of Landsat 7
```


# 3. Calculate water index - Landsat 8/9 data

Bands of interest to calculate water index
- for Landsat 8/9 data, these are band 3 (green), 4 (red), 5 (NIR), 6 (SWIR 1) and 7 (SWIR 2)

Landsat 8/9 data:
- Cumbung - 2013-2019, 2021, 2022, 2023, 2024
- Booligal 093083 - 2013-2022
- Booligal 093084 - 2013-2022

```{r Calculate water index - Landsat 8/9 - Cumbung}
# 2013
wi_cumbung_2013 <- overlay(cumbung_list[["L8_094084_20131125_B3"]], cumbung_list[["L8_094084_20131125_B4"]], cumbung_list[["L8_094084_20131125_B5"]], cumbung_list[["L8_094084_20131125_B6"]], cumbung_list[["L8_094084_20131125_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2013)


# 2014
wi_cumbung_2014 <- overlay(cumbung_list[["L8_094084_20141112_B3"]], cumbung_list[["L8_094084_20141112_B4"]], cumbung_list[["L8_094084_20141112_B5"]], cumbung_list[["L8_094084_20141112_B6"]], cumbung_list[["L8_094084_20141112_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2014)


# 2015
wi_cumbung_2015 <- overlay(cumbung_list[["L8_094084_20151115_B3"]], cumbung_list[["L8_094084_20151115_B4"]], cumbung_list[["L8_094084_20151115_B5"]], cumbung_list[["L8_094084_20151115_B6"]], cumbung_list[["L8_094084_20151115_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2015)


# 2016
wi_cumbung_2016 <- overlay(cumbung_list[["L8_094084_20161117_B3"]], cumbung_list[["L8_094084_20161117_B4"]], cumbung_list[["L8_094084_20161117_B5"]], cumbung_list[["L8_094084_20161117_B6"]], cumbung_list[["L8_094084_20161117_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2016)


# 2017
wi_cumbung_2017 <- overlay(cumbung_list[["L8_094084_20171120_B3"]], cumbung_list[["L8_094084_20171120_B4"]], cumbung_list[["L8_094084_20171120_B5"]], cumbung_list[["L8_094084_20171120_B6"]], cumbung_list[["L8_094084_20171120_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2017)


# 2018 - missing?
wi_cumbung_2018 <- overlay(cumbung_list[["L8_094084_20181022_B3"]], cumbung_list[["L8_094084_20181022_B4"]], cumbung_list[["L8_094084_20181022_B5"]], cumbung_list[["L8_094084_20181022_B6"]], cumbung_list[["L8_094084_20181022_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2018)


# 2019
wi_cumbung_2019 <- overlay(cumbung_list[["L8_094084_20191110_B3"]], cumbung_list[["L8_094084_20191110_B4"]], cumbung_list[["L8_094084_20191110_B5"]], cumbung_list[["L8_094084_20191110_B6"]], cumbung_list[["L8_094084_20191110_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2019)


# 2021
wi_cumbung_2021 <- overlay(cumbung_list[["L8_094084_20211030_B3"]], cumbung_list[["L8_094084_20211030_B4"]], cumbung_list[["L8_094084_20211030_B5"]], cumbung_list[["L8_094084_20211030_B6"]], cumbung_list[["L8_094084_20211030_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2021)


# 2022
wi_cumbung_2022 <- overlay(cumbung_list[["L8_094084_20221118_B3"]], cumbung_list[["L8_094084_20221118_B4"]], cumbung_list[["L8_094084_20221118_B5"]], cumbung_list[["L8_094084_20221118_B6"]], cumbung_list[["L8_094084_20221118_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2022)


# 2023
wi_cumbung_2023 <- overlay(cumbung_list[["L8_094084_20231105_B3"]], cumbung_list[["L8_094084_20231105_B4"]], cumbung_list[["L8_094084_20231105_B5"]], cumbung_list[["L8_094084_20231105_B6"]], cumbung_list[["L8_094084_20231105_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2023)

# 2024
wi_cumbung_2024 <- overlay(cumbung_list[["L9_094084_20241030_B3"]], cumbung_list[["L9_094084_20241030_B4"]], cumbung_list[["L9_094084_20241030_B5"]], cumbung_list[["L9_094084_20241030_B6"]], cumbung_list[["L9_094084_20241030_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_cumbung_2024)
```

```{r Calculate water index - Landsat 8/9 - Booligal 093083}
# 2013
wi_bool_2013_1 <- overlay(booligal_list[["L8_093083_20131118_B3"]], booligal_list[["L8_093083_20131118_B4"]], booligal_list[["L8_093083_20131118_B5"]], booligal_list[["L8_093083_20131118_B6"]], booligal_list[["L8_093083_20131118_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2013_1)

# 2014
wi_bool_2014_1 <- overlay(booligal_list[["L8_093083_20141121_B3"]], booligal_list[["L8_093083_20141121_B4"]], booligal_list[["L8_093083_20141121_B5"]], booligal_list[["L8_093083_20141121_B6"]], booligal_list[["L8_093083_20141121_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2014_1)

# 2015
wi_bool_2015_1 <- overlay(booligal_list[["L8_093083_20151023_B3"]], booligal_list[["L8_093083_20151023_B4"]], booligal_list[["L8_093083_20151023_B5"]], booligal_list[["L8_093083_20151023_B6"]], booligal_list[["L8_093083_20151023_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2015_1)

# 2016
wi_bool_2016_1 <- overlay(booligal_list[["L8_093083_20161110_B3"]], booligal_list[["L8_093083_20161110_B4"]], booligal_list[["L8_093083_20161110_B5"]], booligal_list[["L8_093083_20161110_B6"]], booligal_list[["L8_093083_20161110_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2016_1)

# 2017
wi_bool_2017_1 <- overlay(booligal_list[["L8_093083_20171129_B3"]], booligal_list[["L8_093083_20171129_B4"]], booligal_list[["L8_093083_20171129_B5"]], booligal_list[["L8_093083_20171129_B6"]], booligal_list[["L8_093083_20171129_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2017_1)

# 2018
wi_bool_2018_1 <- overlay(booligal_list[["L8_093083_20181116_B3"]], booligal_list[["L8_093083_20181116_B4"]], booligal_list[["L8_093083_20181116_B5"]], booligal_list[["L8_093083_20181116_B6"]], booligal_list[["L8_093083_20181116_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2018_1)

# 2019
wi_bool_2019_1 <- overlay(booligal_list[["L8_093083_20191119_B3"]], booligal_list[["L8_093083_20191119_B4"]], booligal_list[["L8_093083_20191119_B5"]], booligal_list[["L8_093083_20191119_B6"]], booligal_list[["L8_093083_20191119_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2019_1)

# 2020
wi_bool_2020_1 <- overlay(booligal_list[["L8_093083_20201020_B3"]], booligal_list[["L8_093083_20201020_B4"]], booligal_list[["L8_093083_20201020_B5"]], booligal_list[["L8_093083_20201020_B6"]], booligal_list[["L8_093083_20201020_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2020_1)

# 2021
wi_bool_2021_1 <- overlay(booligal_list[["L8_093083_20211023_B3"]], booligal_list[["L8_093083_20211023_B4"]], booligal_list[["L8_093083_20211023_B5"]], booligal_list[["L8_093083_20211023_B6"]], booligal_list[["L8_093083_20211023_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2021_1)

# 2022
wi_bool_2022_1 <- overlay(booligal_list[["L8_093083_20221010_B3"]], booligal_list[["L8_093083_20221010_B4"]], booligal_list[["L8_093083_20221010_B5"]], booligal_list[["L8_093083_20221010_B6"]], booligal_list[["L8_093083_20221010_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2022_1)
```


```{r Calculate water index - Landsat 8/9 - Booligal 093084}
# 2013
wi_bool_2013_2 <- overlay(booligal_list[["L8_093084_20131118_B3"]], booligal_list[["L8_093084_20131118_B4"]], booligal_list[["L8_093084_20131118_B5"]], booligal_list[["L8_093084_20131118_B6"]], booligal_list[["L8_093084_20131118_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2013_2)

# 2014
wi_bool_2014_2 <- overlay(booligal_list[["L8_093084_20141121_B3"]], booligal_list[["L8_093084_20141121_B4"]], booligal_list[["L8_093084_20141121_B5"]], booligal_list[["L8_093084_20141121_B6"]], booligal_list[["L8_093084_20141121_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2014_2)

# 2015
wi_bool_2015_2 <- overlay(booligal_list[["L8_093084_20151108_B3"]], booligal_list[["L8_093084_20151108_B4"]], booligal_list[["L8_093084_20151108_B5"]], booligal_list[["L8_093084_20151108_B6"]], booligal_list[["L8_093084_20151108_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2015_2)

# 2016
wi_bool_2016_2 <- overlay(booligal_list[["L8_093084_20161110_B3"]], booligal_list[["L8_093084_20161110_B4"]], booligal_list[["L8_093084_20161110_B5"]], booligal_list[["L8_093084_20161110_B6"]], booligal_list[["L8_093084_20161110_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2016_2)

# 2017 
wi_bool_2017_2 <- overlay(booligal_list[["L8_093083_20171129_B3"]], booligal_list[["L8_093083_20171129_B4"]], booligal_list[["L8_093083_20171129_B5"]], booligal_list[["L8_093083_20171129_B6"]], booligal_list[["L8_093083_20171129_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2017_2)

# 2018
wi_bool_2018_2 <- overlay(booligal_list[["L8_093084_20181116_B3"]], booligal_list[["L8_093084_20181116_B4"]], booligal_list[["L8_093084_20181116_B5"]], booligal_list[["L8_093084_20181116_B6"]], booligal_list[["L8_093084_20181116_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2018_2)

# 2019
wi_bool_2019_2 <- overlay(booligal_list[["L8_093084_20191119_B3"]], booligal_list[["L8_093084_20191119_B4"]], booligal_list[["L8_093084_20191119_B5"]], booligal_list[["L8_093084_20191119_B6"]], booligal_list[["L8_093084_20191119_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2019_2)

# 2020
wi_bool_2020_2 <- overlay(booligal_list[["L8_093084_20201020_B3"]], booligal_list[["L8_093084_20201020_B4"]], booligal_list[["L8_093084_20201020_B5"]], booligal_list[["L8_093084_20201020_B6"]], booligal_list[["L8_093084_20201020_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2020_2)

# 2021
wi_bool_2021_2 <- overlay(booligal_list[["L8_093084_20211023_B3"]], booligal_list[["L8_093084_20211023_B4"]], booligal_list[["L8_093084_20211023_B5"]], booligal_list[["L8_093084_20211023_B6"]], booligal_list[["L8_093084_20211023_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2021_2)

# 2022 
wi_bool_2022_2 <- overlay(booligal_list[["L8_093084_20221010_B3"]], booligal_list[["L8_093084_20221010_B4"]], booligal_list[["L8_093084_20221010_B5"]], booligal_list[["L8_093084_20221010_B6"]], booligal_list[["L8_093084_20221010_B7"]], fun = function(B3, B4, B5, B6, B7) {
  return(1.7204+171*B3+3*B4-70*B5-45*B6-71*B7)
})
plot(wi_bool_2022_2)
```




# 4. Merge Booligal images

```{r Merge Booligal images}
wi_bool_2010 <- merge(wi_bool_2010_1, wi_bool_2010_2)
wi_bool_2011 <- merge(wi_bool_2011_1, wi_bool_2011_2)
wi_bool_2012 <- merge(wi_bool_2012_1, wi_bool_2012_2)
wi_bool_2013 <- merge(wi_bool_2013_1, wi_bool_2013_2)
wi_bool_2014 <- merge(wi_bool_2014_1, wi_bool_2014_2)
wi_bool_2015 <- merge(wi_bool_2015_1, wi_bool_2015_2)
wi_bool_2016 <- merge(wi_bool_2016_1, wi_bool_2016_2)
wi_bool_2017 <- merge(wi_bool_2017_1, wi_bool_2017_2)
wi_bool_2018 <- merge(wi_bool_2018_1, wi_bool_2018_2)
wi_bool_2019 <- merge(wi_bool_2019_1, wi_bool_2019_2)
wi_bool_2020 <- merge(wi_bool_2020_1, wi_bool_2020_2)
wi_bool_2021 <- merge(wi_bool_2021_1, wi_bool_2021_2)
wi_bool_2022 <- merge(wi_bool_2022_1, wi_bool_2022_2)
```


# 5. Write rasters

```{r Write water index rasters - cumbung}
# write rasters
setwd("C:/Users/z5204897/OneDrive - UNSW/Desktop/RA/Projects/2023_Lachlan_waterbird_and_flood_datasets_compilation/R/waterbird_lachlan")

writeRaster(wi_cumbung_2010,filename = "Export/wi_cumbung_20101203.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2011,filename = "Export/wi_cumbung_20111104.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2012,filename = "Export/wi_cumbung_20121114.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2013,filename = "Export/wi_cumbung_20131125.tif", format="GTiff", overwrite = TRUE)
#writeRaster(wi_cumbung_2014,filename = "Export/wi_cumbung_20141112.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2015,filename = "Export/wi_cumbung_20151115.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2016,filename = "Export/wi_cumbung_20161117.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2017,filename = "Export/wi_cumbung_20171104.tif", format="GTiff", overwrite = TRUE)
#writeRaster(wi_cumbung_2018,filename = "Export/wi_cumbung_20181022.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2019,filename = "Export/wi_cumbung_20191110.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2020,filename = "Export/wi_cumbung_20201018.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2021,filename = "Export/wi_cumbung_20211030.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2022,filename = "Export/wi_cumbung_20221118.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2023,filename = "Export/wi_cumbung_20231105.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2024,filename = "Export/wi_cumbung_20241030.tif", format="GTiff", overwrite = TRUE)
```

```{r Write water index rasters - booligal}
writeRaster(wi_bool_2010,filename = "Export/wi_bool_20101008.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2011,filename = "Export/wi_bool_20111011.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2012,filename = "Export/wi_bool_20121022.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2013,filename = "Export/wi_bool_20131118.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2014,filename = "Export/wi_bool_20141121.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2015,filename = "Export/wi_bool_20151023-1108.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2016,filename = "Export/wi_bool_20161110.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2017,filename = "Export/wi_bool_20171129.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2018,filename = "Export/wi_bool_20181116.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2019,filename = "Export/wi_bool_20191119.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2020,filename = "Export/wi_bool_20201020.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2021,filename = "Export/wi_bool_20211023.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_bool_2022,filename = "Export/wi_bool_20221010_2.tif", format="GTiff", overwrite = TRUE)
```


```{r Write reclassified rasters}
# write rasters
setwd("C:/Users/z5204897/OneDrive - UNSW/Desktop/RA/Projects/2023_Lachlan_waterbird_and_flood_datasets_compilation/R/waterbird_lachlan")

writeRaster(wi_cumbung_20141112_reclass,filename = "Export/wi_cumbung_20141112_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2015_reclass,filename = "Export/wi_cumbung_20151115_reclass.tif", format="GTiff", overwrite = TRUE)

writeRaster(wi_cumbung_2010_reclass,filename = "Export/wi_cumbung_20101117_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2011_reclass,filename = "Export/wi_cumbung_20111104_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2012_reclass,filename = "Export/wi_cumbung_20121106_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2013_reclass,filename = "Export/wi_cumbung_20131125_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2016_reclass,filename = "Export/wi_cumbung_20161117_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2017_reclass,filename = "Export/wi_cumbung_20171120_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2018_reclass,filename = "Export/wi_cumbung_20181022_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2019_reclass,filename = "Export/wi_cumbung_20191110_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2020_reclass,filename = "Export/wi_cumbung_20201018_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2021_reclass,filename = "Export/wi_cumbung_20211030_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2022_reclass,filename = "Export/wi_cumbung_20221118_reclass.tif", format="GTiff", overwrite = TRUE)
writeRaster(wi_cumbung_2022_reclass,filename = "Export/wi_cumbung_20221118_reclass.tif", format="GTiff", overwrite = TRUE)
```







